Growing up with Nell: A Narrative Interface for Literacy

### 2012-03-09 paper.tex
Tweak bibliography.

\subsection{Extensible dialog with AIML}
The child can interact with the Princess, and other agents within
Nell, directly.  Convincing discourse is a hard problem, but
reasonable approximations do not have to be difficult.  We leverage
the AIML language developed for AliceBot~\cite{xxx}, which has
won several Turing contests. \textbf{XXX more precise here XXX}
\footnote{Anecdotal evidence shows that interactions with Eliza-style
  responders can be rewarding: one woman spent hours each day
  conversing with the original Eliza.~\cite{RadioLab}}

@@

The Sugar Learning environment~\cite{XXX} is an earlier effort at
child education.  We've learned directly from this effort.  Nell
focuses on children even further from educational infrastructure.
The narrative at Nell's code attempts to provide students additional
pedagogical guidance, and the direct interaction model avoids keyboard
problems which have plagued Sugar's initial deployments.  Nell also
attempts to provide a greater sense of ownership through pervasive
customization.

>>>>

\subsection{Extensible dialog with AIML}
The child can interact with the Princess, and other agents within
Nell, directly.  Convincing discourse is a hard problem, but
reasonable approximations do not have to be difficult.  We leverage
the AIML language developed for AliceBot~\cite{alicebotxxx}, which has
won several Turing contests. \textbf{XXX more precise here XXX}
\footnote{Anecdotal evidence shows that interactions with Eliza-style
  responders can be rewarding: one woman spent hours each day
  conversing with the original Eliza.~\cite{RadioLab}}

@@

The Sugar Learning environment~\cite{sugarXXX} is an earlier effort at
child education.  We've learned directly from this effort.  Nell
focuses on children even further from educational infrastructure.
The narrative at Nell's code attempts to provide students additional
pedagogical guidance, and the direct interaction model avoids keyboard
problems which have plagued Sugar's initial deployments.  Nell also
attempts to provide a greater sense of ownership through pervasive
customization.
